---
title: "First Assignment"
author: "Data"
date: "06/05/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Please complete all the tasks listed below. After completing the tasks download the .Rmd file and upload in the peer review item for grading.

# Additionally please write text between the code chunks explaining what each code chunk is about.

1.a bulleted list with sub-bullets under at least one item (10 pt)

-   Item 1
    -   Subitem 1.1
    -   Subitem 1.2
-   Item 2
    -   Subitem 2.1
    -   Subitem 2.2

2.a numbered list (10 pt)

1.  Item 1
2.  Item 2
3.  Item 3
4.  Item 4

3.some words italicized (5 pt)

*This is my italized text*

4.some words in bold print (5 pt)

**This is my bold text**

5.two levels of headers (10 pt)

# This is my header 1

## This is my header 2

6.the results of some R code without showing the code (10 pt)

```{r, echo=FALSE}
print("This is my results without showing thw code")
```

7.a table of text at least 3 columns wide and 3 rows long (10 pt)

| header 1 | header 2 | header 3 |
|----------|----------|----------|
| element  | element  | element  |
| element  | element  | element  |
| element  | element  | element  |

8.a plot (show the code that generates the plot) (10 pt)
```{r}
library(datasets)
data(cars)

plot(cars, xlab = "Speed (mph)", ylab = "Stopping distance (ft)")
```

9.your session info (as output from R) (10 pt)

```{r}
print(sessionInfo())
```

10.Execution of .Rmd file (10 pt)

11.Upload and execution of knitted pdf (10 pt)
